Active Learning from Blackbox to Timed Connectors

### 2016-01-18 paper/paper.tex
.

\begin{definition}[Mealy machine]
  A Mealy machine is a 6-tuple $(S, s_0, I, O, \delta, \lambda)$ consisting of:
  \begin{itemize}
    \item[-] a finite set of states $S$
    \item[-] an initial $s_0\in S$
    \item[-] a finite set of inputs $I$
    \item[-] a finite set of outputs $O$
    \item[-] a transition function $\delta : S \times I \rightarrow S$ mapping a pair of a
      state and an input to the corresponding next state.
    \item[-] an output function $\lambda : S \times  I \rightarrow O$ mapping a pair
      of a state and an input to the corresponding output.
  \end{itemize}
\end{definition}

@@

\begin{itemize}
  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) In grammar-learning
    \cite{DBLP:journals/iandc/Angluin87}) \emph{mq} checks if a word is a member of certain language
    defined by the given grammar. When it comes to
    automata learning, \emph{mq} is supposed to provide \emph{simulation results} for given input
    sequences.
  \item[-] \textbf{Equivalence Query} (hereinaftr referred to as \emph{eq}) Given a hypothesis
    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
    equivalent to the system-under-learn and generates a counter-example if needed. Generally, 
    \emph{eq} is irrealizable when SUL is a blackbox. So we tactically use $mq$ to achieve the
    approximate results.
\end{itemize}

@@

As presented in section \ref{sec:reo}, all real-time behavior in timed Reo comes with a finite set
of timed channels, and the number of these channels are apparently finite. We use
$t_i\in\mathbb{Q}, i=1,2,\dots,n$ to denote the delays of these timed channels, and then we can define a precision
function $prec$:
\[
prec(t_1,\cdots,t_n) = \max_T\{T\in\mathbb{Q}|\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
\]
It's easy to prove that such a $T$ always exists.

In real systems, the concept \emph{time precision} is well known with other names like ``clock-period''.
Most of the time, we know the clock-period of some hardware components, even without any idea of its
structure. With such precision $dt$ given, it's reasonable to assume that all $t$-timers are actually
$ndt$-timers. In following sections, we'll use $n$-Timers instead.

@@

\subsection{Parameterized Mealy Machine}
We present a model named \emph{parameterized Mealy machine}to model timed connectors. PMM is
supposed to behave as a bridge between Mealy machines and timed connectors. Connectors are firstly
defined as PMMs, and composed by production operator and link operator. Then, concrete Mealy-machine
model can be generated from the PMM model.
Following the formal definition of Mealy machine in Section \ref{sec:preliminaries}, we define the
\emph{parameterized Mealy machine} as follows.

\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a 6-tuple $\mathcal{PM}=\langle
  S, s_0, I, O, \delta, \lambda\rangle$ with a parameter named $\Sigma$ where 
  \begin{itemize}
    \item[-] $\Sigma$, the parameter, is a \emph{finite} datum alphabet
    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $I$ is a finite set of source-ends.
    \item[-] $O$ is a finite set of sink-ends.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow Output(\Sigma,I,O)$ to denote the
      output function.
    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow S(\Sigma)$ to denote the transiton
      function.
  \end{itemize}
\end{definition}

In the definition above, \emph{Input} and \emph{Output} are used to generate input actions
and output actions from the corresponding alphabets and source/sink ends. The value of $Input(\Sigma,I,O)$ is
defined as a set of functions on $I\cup O$ where $\forall f\in Input(\Sigma,I,O)$ and an additional
\emph{time action} T, we have
\[
\forall i\in I\backslash\{T\}, f(i)\in \Sigma\cup\{\bot\}\land \forall o\in
O,f(o)\in\{\rread, \rnoread\}
\]
where we use $\rread$ to indicate that an end-sink is ready for write, and $\rnoread$ otherwise. Note
that a $\bot$ means that there is \emph{no} data items on a source (or sink) end. In the same way,
$Output(\Sigma,I,O)$ is defined as a set of functions on domain $O$, with an additional symbol
$\rblock$ indicating an input failure. Similarly, $\forall f\in Output(\Sigma,I,O), f\neq \rblock$
implies
\[
\forall o\in O, f(o)\in \Sigma\cup\{\bot\}
\]

\begin{example}[Input and Output]
  If we have a simple alphabet with only one item $d_0$, a source-end named $A$, and a
  sink-end named $B$, the input actions would be
  \begin{small}
    \begin{eqnarray*}
      Input(\{d_0\},\{A\},\{B\}) &=& \{\{A:d_0,B:\rread\},\{A:d_0,B:\rnoread\}, \\
      & & \{A:\bot,B:\rread\},\{A:\bot,B:\rnoread\},T\}
    \end{eqnarray*}
  \end{small}
  and its output actions
  \[
  Output(\{d_0\},\{A\},\{B\}) =\{\{B:d_0\},\{B:\bot\}, \rblock\}
  \]
\end{example}

If there is no data item written to any sink ends, we use $\varnothing$ to denote such an empty
output. For example, in the case given above, $\{B:\bot\}$ can be briefly rewritten as $\varnothing$.

Parameterized Mealy machines can be seen as an abstract form of Mealy machines, which means that we
still need a convert function between the two models.

\begin{definition}[Concretize Mapping]
  We use $\smap{\mathcal{PM}}_{\Sigma}$ to denote the concrete Mealy machine which is determined by
  an abstract parameterized Mealy machine $\mathcal{PM}$ and the alphabet $\Sigma$. Apparently
  $\smap{\mathcal{PM}}_{\Sigma}$ can be described as
  \begin{eqnarray*}
    \smap{\mathcal{PM}}_{\Sigma} &=& 
    \langle
    \mathcal{PM}.S(\Sigma), \mathcal{PM}.s_0, \\
    & & Input(\Sigma, \mathcal{PM}.I), Output(\Sigma, \mathcal{PM}.O), \\
    & & \mathcal{PM}.\delta(\Sigma), \mathcal{PM}.\lambda(\Sigma),
    \rangle
  \end{eqnarray*}
\end{definition}

Now we can use parameterized Mealy Machines to define a new semantics for timed Reo. Here we
take one asynchronous channel (FIFO1), one asynchronous channel (Sync) and one timed channel (Timer)
as examples.

\begin{example}[PMM Semantics of FIFO1 channel]
  \label{example:pmmfifo}
  The semantics of FIFO channel with source end $A$ and sink end $B$ can be defined as follows.
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          (B:\bot) & s=q_0\land i=(A:\_,B:\rnoread) \\
          (B:\bot) & s=q_d\land i=(A:\_,B:\rnoread) \\     
          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
          (B:d) & s=q_d\land i=(A:\_,B:\rread)\\
          \rblock & s=q_d\land i=(A:d,B:\rnoread) \\
          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] transition function
      \begin{displaymath}
        \lambda(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

Besides, the concrete Mealy machine (where $\Sigma=\{a\}$) is shown in Figure \ref{fig:pmmfifo},
where labels of edges are in form of $\frac{input}{output}$.
\begin{figure}[ht]
  \begin{center}
    \input{./images/pmmfifo.tex}
  \end{center}
  \caption{PMM-based Semantics of $\smap{FIFO1}_\Sigma$, where $\Sigma=\{a\}$}
  \label{fig:pmmfifo}
\end{figure}

\begin{example}[PMM Semantics of Sync channel]
  The PMM-based semantics of a Sync channel with a source-end A and a sink-end B can be defined as:
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}$, $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          (B:\bot) & s=q_0\land i=(A:\bot,B:\rnoread) \\
          (B:d) & s=q_0\land i=(A:d,B:\rread)\\
          \rblock & s=q_0\land i=(A:\bot,B:\rread) \\
          \rblock & s=q_0\land i=(A:d,B:\rnoread) \\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] transition function $\lambda(\Sigma)(s,i)=q_0$.
  \end{itemize}
\end{example}

\begin{example}[PMM Semantics of n-Timer channel]
  Considering an n-Timer channel with a source-end A and a sink-end B, we define its PMM-based
  semantics as:
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_{i,d}|0\leq i\leq n, d\in \Sigma\}\cup\{q_0\}$
    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          (B:d) & s=q_{n,d}\land i=(A:d,B:\rread)\\
          \rblock & s=q_{n,d}\:\land \\
          & (i=T\lor i=(A:\_,B:\rnoread) \\
          \rblock & s=q_{j,d}\land 1 \leq j < n\land \\
          & (i=(A:\_,B:\rread)\lor \\
          & i=(A:d,B:\_))\\
          (B:\bot) & otherwise\\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] transition function
      \begin{displaymath}
        \lambda(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          q_{j+1,d} & s=q_{j,d}\land i=T\land0 < j < n\\
          q_0 & s=q_{n,d}\land i=(A:\bot,B:\rread) \\
          q_{0,d} & s=q_{n,d'}\land i=(A:d,B:\rread) \\
          q_{0,d} & s=q_0 \land i=(A:d,B:\_) \\
          s & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

Similarly, we can use parameterized mealy machines to define the semantics of other basic timed Reo
channels. Now we're going to show how to compose these channels into complicated connectors.

\begin{definition}[Production Operator]
  Now we're going to define the production operator \emph{prod} of two parameterized Mealy machines as,
  \[
  prod(PM_1,PM_2)=PM_3
  \]
  as follows. Here we assume that $PM_2.O\cap PM_1.I=\varnothing$
  \begin{itemize}
  	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O$
    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_2.I$
  \end{itemize}
  \emph{(Here we assume that sink ends of $PM_1$ can be connected to source ends $PM_2$, but not
  vise versa)}
  \begin{itemize}
    \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
    \item[-] $\forall\Sigma, PM_3.\delta(\Sigma)((s_1,s_2), i)=$
      \begin{displaymath}
        \left\{
        \begin{array}[ht]{ll}
          (Out_1 + Out_2)\downarrow_{PM_3.O} & Out_1\neq\rblock\land Out_2\neq\rblock \\
          \rempty & i = T \\
          \rblock & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
      where we have
      \begin{itemize}
        \item[*] $In_1 = i\downarrow_{PM_1.I}$
        \item[*] $Out_1 = PM_1.\delta(\Sigma)(s_1,In_1)$
        \item[*] $In_2 = (Out_1 + i)\downarrow_{PM_2.I}$
        \item[*] $Out_2 = PM_2.\delta(\Sigma)(s_2,In_2)$
      \end{itemize}
    \item[-] $\forall\Sigma, PM_3. \lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
      where we have
      \begin{itemize}
        \item[*] $s_1' = PM_1.\lambda(\Sigma)(s_1,In_1)$
        \item[*] $s_2' = PM_2.\lambda(\Sigma)(s_2,In_2)$
      \end{itemize}
  \end{itemize}
\end{definition}

@@

\begin{algorithm} 
  \caption{CloseTable} 
  \label{alg:buildtable}
  \KwIn{Oracle interface $mq$, Input actions $\mathcal{I}$, suffix set $D$}
  \KwOut{Observation table $obs$} 
  $obs$ initialized as empty\;
  $unclosed=\{\varepsilon\}$\;
  \Repeat{$unclosed=\varnothing$}
  {
    $next=\{st|\forall s\in unclosed,\forall t\in \mathcal{I}\}$\;
    append $unclosed$ to $obs$\;
    $unclosed=\{seq\in next|\forall a\in obs, seq \not\sim_D a\}$\;
  }
  \Return $obs$\; 
\end{algorithm}

>>>>

\begin{definition}[Mealy machine]
  A Mealy machine is a 6-tuple $(S, s_0, I, O, \delta, \lambda)$ consisting of:
  \begin{itemize}
    \item[-] a finite set of states $S$
    \item[-] an initial $s_0\in S$
    \item[-] a finite set of inputs $I$
    \item[-] a finite set of outputs $O$
    \item[-] an output function $\delta : S \times  I \rightarrow O$ mapping a pair
      of a state and an input to the corresponding output.
    \item[-] a transition function $\lambda : S \times I \rightarrow S$ mapping a pair of a
      state and an input to the corresponding successor state.
  \end{itemize}
\end{definition}

@@

\begin{itemize}
  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) In grammar-learning
    \cite{DBLP:journals/iandc/Angluin87}) \emph{mq} checks if a word is a member of certain language
    defined by the given grammar. When it comes to
    automata learning, \emph{mq} is supposed to provide \emph{simulation results} for given input
    sequences.
  \item[-] \textbf{Equivalence Query} (hereinafter referred to as \emph{eq}) Given a hypothesis
    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
    equivalent to the system-under-learn and generates a counter-example if needed. Generally, 
    \emph{eq} is irrealizable when SUL is a blackbox. So we tactically use $mq$ to achieve the
    approximate results.
\end{itemize}

@@

As presented in section \ref{sec:reo}, all real-time behavior in timed Reo comes with a finite set
of timed channels, and the number of these channels are apparently finite. We use
$t_i\in\mathbb{Q}, i=1,2,\dots,n$ to denote the delays of these timed channels, and then we can define a precision
function $prec$ which calculate a gcd-style \emph{maximal time precision}:
\[
prec(t_1,\dots,t_n) = \max\{T\in\mathbb{Q}|\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
\]
It's easy to prove that such a $T$ always exists.

In embedded systems, the maximal time precision is also called ``clock-period'', which is the basic
time unit provided by an oscillator. For example, a widely-used Intel-80C51 microcontroller works
under the frequency 16Mhz, where the clock-period is $62.5$ns. A resonable assumption comes that
such a maximal time precision $dt=prec(t_1,\dots,t_n)$ should always be provided to make sure
different components are able to work together. Then all $t_i$-Timers can be seen as $n_idt$-Timers
for some $n_i$. In the following sections, we'll use $n_i$-Timers instead.

@@

\subsection{Parameterized Mealy Machine}
We present a model named \emph{parameterized Mealy machine} to model timed connectors. PMM is
supposed to behave as a bridge between Mealy machines and timed connectors. Connectors are firstly
defined as PMMs, and composed by production operator and link operator. Then, concrete Mealy-machine
model can be generated from the PMM model.
Following the formal definition of Mealy machine in Section \ref{sec:preliminaries}, we define the
\emph{parameterized Mealy machine} as follows.

\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} with a parameter $\Sigma$ is defined as a 6-tuple
  $\mathcal{PM}=\langle S, s_0, I, O, \delta, \lambda\rangle$ where 
  \begin{itemize}
    \item[-] The value of $\Sigma$ is a \emph{finite} data set (hereinafter referred as
      alphabet), e.g. $\{a,b\}$
    \item[-] $S$ maps an alphabet to a \emph{finite} set of states.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma.s_0\in S(\Sigma)$
    \item[-] $I$ is a finite set of source-ends.
    \item[-] $O$ is a finite set of sink-ends.
    \item[-] $\delta$ maps an alphabet to an \emph{output function}. We use
      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow Output(\Sigma,O)$ to denote the
      output function.
    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I,O)\rightarrow S(\Sigma)$ to denote the
      transition function.
  \end{itemize}
\end{definition}

In the definition above, \emph{Input} and \emph{Output} are used to generate the set of input actions
and output actions from the corresponding alphabets and source/sink ends. $Input(\Sigma,I,O)$ is
defined as a set of functions on $I\cup O$ and an additional \emph{time action} T,  
where for all $f\in Input(\Sigma,I,O)\backslash \{T\}$ we have
\[
\forall i\in I.f(i)\in \Sigma\cup\{\bot\}\land \forall o\in O.f(o)\in\{\rread, \rnoread\}
\]
where we use $\bot$ to indicate that there is \emph{no} data item on a channel end. 
Besides, $\rread$ means that a sink end is ready for writing, $\rnoread$ otherwise. 
In the same way,
$Output(\Sigma,O)$ is defined as a set of functions on $O$, with an additional symbol
$\rblock$ indicating an input failure. Similarly, for all $f\in
Output(\Sigma,O)\backslash\{\rblock\}$,
\[
\forall o\in O. f(o)\in \Sigma\cup\{\bot\}
\]

\begin{example}[Input and Output]
  If we have a simple alphabet with only one item $d_0$, a source-end named $A$, and a
  sink-end named $B$, the input actions would be
  \begin{eqnarray*}
    & & Input(\{d_0\},\{A\},\{B\}) \\
    & = & \{\{A\mapsto d_0,B\mapsto\rread\},\{A\mapsto d_0,B\mapsto\rnoread\}, \\
    & & \{A\mapsto\bot,B\mapsto\rread\}, \{A\mapsto\bot,B\mapsto\rnoread\},T\}
  \end{eqnarray*}
  and its output actions
  \[
  Output(\{d_0\},\{A\},\{B\}) =\{\{B\mapsto d_0\},\{B\mapsto \bot\}, \rblock\}
  \]
\end{example}

We use $\varnothing$ to denote the empty output when no data item is written to any sink end.
For example, in this case $\{B\mapsto\bot\}$ can be briefly denoted as $\rempty$.

Parameterized Mealy machines can be seen as an abstraction of Mealy machines, and we
still need a convert function between the two models.

\begin{definition}[Concretize Mapping]
  We use $\smap{\mathcal{PM}}_{\Sigma}$ to denote the concrete Mealy machine which is determined by
  an abstract parameterized Mealy machine $\mathcal{PM}$ and the alphabet $\Sigma$. Apparently
  $\smap{\mathcal{PM}}_{\Sigma}$ can be described as
  \begin{eqnarray*}
    \smap{\mathcal{PM}}_{\Sigma} &=& 
    \langle
    \mathcal{PM}.S(\Sigma), \mathcal{PM}.s_0, \\
    & & Input(\Sigma, \mathcal{PM}.I, \mathcal{PM}.O), Output(\Sigma, \mathcal{PM}.O), \\
    & & \mathcal{PM}.\delta(\Sigma), \mathcal{PM}.\lambda(\Sigma),
    \rangle
  \end{eqnarray*}
\end{definition}

Now we can use PMMs to specify timed Reo. Here we take the asynchronous channel (FIFO1), the
synchronous channel (Sync) and the timed channel (Timer) as examples. For simplicity, we use $A=\_$
to indicate that there is no constraint on channel end $A$.

\begin{example}[FIFO1]
  \label{example:pmmfifo}
  The PMM of a FIFO1 with source end $A$ and sink end $B$ can be defined as follows.
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}\cup\{q_d|d\in\Sigma\}$
    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \small
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          \rempty & s=q_0\land i=\{A\mapsto\_,B\mapsto\rnoread\} \\
          \rblock & s=q_0\land i=\{A\mapsto d',B\mapsto\rread\} \\
          \rblock & s=q_0\land i=\{A\mapsto\bot,B\mapsto\rread\} \\
          \rempty & s=q_d\land i=\{A\mapsto\bot,B\mapsto\rnoread\} \\     
          \{B\mapsto d\} & s=q_d\land i=\{A\mapsto\_,B\mapsto\rread\}\\
          \rblock & s=q_d\land i=\{A\mapsto d',B\mapsto \rnoread\} \\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] transition function
      \begin{displaymath}
        \small
        \lambda(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          q_{d'} & s=q_0\land i=\{A\mapsto d',B\mapsto\_\} \\
          q_{d'} & s=q_{d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
          q_{d} & s=q_{d}\land i=\{A\mapsto \_,B\mapsto \rnoread\} \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

Besides, the concrete Mealy machine (where $\Sigma=\{d\}$) is shown in Figure \ref{fig:pmmfifo},
where labels of edges are in form of $\frac{input}{output}$. All $\rblock$ edges are ignored for
clearance.
\begin{figure}[ht]
  \begin{center}
    \input{./images/pmmfifo.tex}
  \end{center}
  \caption{PMM-based Semantics of $\smap{FIFO1}_\Sigma$, where $\Sigma=\{d\}$}
  \label{fig:pmmfifo}
\end{figure}

\begin{example}[Sync]
  The PMM of a Sync with a source-end A and a sink-end B can be defined as:
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_0\}$, $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          \rempty & i=\{A\mapsto\bot,B\mapsto\rnoread\} \\
          \{B\mapsto d\} & i=\{A\mapsto d,B\mapsto\rread\}\\
          \rblock & i=\{A\mapsto\bot,B\mapsto\rread\} \\
          \rblock & i=\{A\mapsto d,B\mapsto\rnoread\} \\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] transition function $\lambda(\Sigma)(s,i)=q_0$.
  \end{itemize}
\end{example}

\begin{example}[n-Timer]
  The PMM of an n-Timer with a source-end A and a sink-end B can be defined as:
  \begin{itemize}
    \item[-] $S(\Sigma)=\{q_{i,d}|0\leq i\leq n, d\in \Sigma\}\cup\{q_0\}$
    \item[-] $I=\{A\}$, $O=\{B\}$, $s_0=q_0$
    \item[-] output function
      \begin{displaymath}
        \small
        \delta(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          \{B\mapsto d\} & s=q_{n,d}\land i=\{A\mapsto \_,B\mapsto \rread\}\\
          \rblock & s=q_{n,d}\land \\
          & (i=T\lor i=\{A\mapsto \_,B\mapsto \rnoread\}) \\
          \rblock & s=q_{j,d}\land 0 \leq j < n\land \\
          & (i=\{A\mapsto \_,B\mapsto \rread\}\lor \\
          & i=\{A\mapsto d,B\mapsto \_\})\\
          \rempty & otherwise\\
        \end{array}
        \right.
      \end{displaymath} 
    \item[-] transition function
      \begin{displaymath}
        \small
        \lambda(\Sigma)(s,i)=\left\{
        \begin{array}[ht]{ll}
          q_{0,d} & s=q_0 \land i=\{A\mapsto d,B\mapsto \_\} \\
          q_{j+1,d} & s=q_{j,d}\land i=T\land0 \leq j < n\\
          q_0 & s=q_{n,d}\land i=\{A\mapsto \bot,B\mapsto \rread\} \\
          q_{0,d'} & s=q_{n,d}\land i=\{A\mapsto d',B\mapsto \rread\} \\
          q_0 & s=q_{n,d} \land i=T \\
          s & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{example}

Similarly, we can use PMMs to describe the behavior of other basic timed Reo
channels. Now we show how to compose these channels into more complicated connectors.

\begin{definition}[Production]
  Now we're going to define the production operator \emph{prod} of two parameterized Mealy machines
  \[
  prod(PM_1,PM_2)=PM_3
  \]
  as follows. Here we assume that $PM_2.O\cap PM_1.I=\varnothing$
  \begin{itemize}
  	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O$
    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_2.I$
  \end{itemize}
  \emph{(Here we assume that sink ends of $PM_1$ can be connected to source ends $PM_2$, but not
  vise versa)}
  \begin{itemize}
    \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
    \item[-] $\forall\Sigma, PM_3.\delta(\Sigma)((s_1,s_2), i)=$
      \begin{displaymath}
        \left\{
        \begin{array}[ht]{ll}
          (Out_1 + Out_2)\downarrow_{PM_3.O} & Out_1\neq\rblock\land Out_2\neq\rblock \\
          \rempty & i = T \\
          \rblock & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
      where we have
      \begin{itemize}
        \item[*] $In_1 = i\downarrow_{PM_1.I}$
        \item[*] $Out_1 = PM_1.\delta(\Sigma)(s_1,In_1)$
        \item[*] $In_2 = (Out_1 + i)\downarrow_{PM_2.I}$
        \item[*] $Out_2 = PM_2.\delta(\Sigma)(s_2,In_2)$
      \end{itemize}
    \item[-] $\forall\Sigma, PM_3. \lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
      where we have
      \begin{itemize}
        \item[*] $s_1' = PM_1.\lambda(\Sigma)(s_1,In_1)$
        \item[*] $s_2' = PM_2.\lambda(\Sigma)(s_2,In_2)$
      \end{itemize}
  \end{itemize}
\end{definition}

@@

\begin{algorithm} 
  \caption{CloseTable} 
  \label{alg:buildtable}
  \small
  \KwIn{Oracle interface $mq$, Input actions $\mathcal{I}$, suffix set $D$}
  \KwOut{Observation table $obs$} 
  $obs$ initialized as empty\;
  $unclosed=\{\varepsilon\}$\;
  \Repeat{$unclosed=\varnothing$}
  {
    $next=\{st|\forall s\in unclosed,\forall t\in \mathcal{I}\}$\;
    append $unclosed$ to $obs$\;
    $unclosed=\{seq\in next|\forall a\in obs, seq \not\sim_D a\}$\;
  }
  \Return $obs$\; 
\end{algorithm}
